---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ElizabethWarrenMeme

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ElizabethWarrenMeme)](https://cran.r-project.org/package=ElizabethWarrenMeme)
[![Travis build status](https://travis-ci.org/EmilHvitfeldt/ElizabethWarrenMeme.svg?branch=master)](https://travis-ci.org/EmilHvitfeldt/ElizabethWarrenMeme)
[![Codecov test coverage](https://codecov.io/gh/EmilHvitfeldt/ElizabethWarrenMeme/branch/master/graph/badge.svg)](https://codecov.io/gh/EmilHvitfeldt/ElizabethWarrenMeme?branch=master)
<!-- badges: end -->

I resently came across this humorous [twitter thread](https://twitter.com/triciamatthew/status/1144051004352225281) about [Elizabeth Warren](https://en.wikipedia.org/wiki/Elizabeth_Warren). This package includes the fun responses and a function to access a a quotes.

## Installation

You can install the development version of ElizabethWarrenMeme from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("EmilHvitfeldt/ElizabethWarrenMeme")
```

## Example

All the quotes are availiable with the `all_elizabeth_warren()` function

```{r}
library(ElizabethWarrenMeme)
head(all_elizabeth_warren())
```

but if you are feeling adventuraous you can use the `elizabeth_warran()` to get a random quote,

```{r}
elizabeth_warran()
```

or specify a id to get a specific quote.

```{r}
elizabeth_warran(104)
elizabeth_warran(107)
elizabeth_warran(108)
```

## Code of Conduct

Please note that the 'ElizabethWarrenMeme' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
